curling

### 2021-01-21 inst/curling.Rmd
tidy URLs (which were wrong)

## Curling

Curling is a sport with stones and brooms.  Following dataset taken
from [wikipedia](https://www.google.com "Google's Homepage"), women's
tournament:

@@

>>>>

[Curling](https://en.wikipedia.org/wiki/Curling) is a sport with
stones and brooms.  Following dataset taken from
[wikipedia](https://en.wikipedia.org/w/index.php?title=Curling_at_the_Winter_Olympics&oldid=998891075),
women's tournament:

@@

### References

Curling at the Winter Olympics, https://en.wikipedia.org/w/index.php?title=Curling_at_the_Winter_Olympics&oldid=998891075 (last visited Jan. 21, 2021).
